% Resume for Meta AI Security Positions - Single Page
% Dongkwan Kim

\documentclass[11pt,letterpaper]{article}
\usepackage[utf8]{inputenc}
\usepackage[margin=0.6in]{geometry}
\usepackage{enumitem}
% \usepackage{hyperref}
\usepackage{titlesec}
% \usepackage{fontawesome5}
% \usepackage{fontspec}
\usepackage{fontawesome5}
\faStyle{regular}

% For pretty color
\usepackage[hyphens]{url}
\usepackage{color}
\definecolor{darkcyan}{cmyk}{0.75,0,0,0}
\definecolor{highlight}{RGB}{220, 20, 60}     % For key metrics
\definecolor{accent}{RGB}{0, 100, 0}         % For achievements
\definecolor{secondary}{RGB}{70, 70, 70}     % For supporting info
\usepackage[breaklinks,colorlinks,urlcolor=darkcyan]{hyperref}
\usepackage{xstring}

% Custom commands for consistent formatting
\newcommand{\metric}[1]{\textcolor{highlight}{#1}}
\newcommand{\achievement}[1]{\textcolor{accent}{#1}}
\newcommand{\jobtitle}[1]{\textbf{#1}}
\newcommand{\location}[1]{\textcolor{secondary}{\small #1}}
\newcommand{\daterange}[1]{\textcolor{secondary}{\small #1}}

% Compact formatting
\titleformat{\section}{\large\bfseries}{}{0em}{}[\titlerule]
% \titlespacing*{\section}{0pt}{6pt}{5pt}
\setlist[itemize]{leftmargin=*,topsep=1pt}
\hypersetup{colorlinks=true,linkcolor=blue,urlcolor=blue}
\setlength{\parindent}{0pt}
\pagestyle{empty}

% \setlist[itemize,1]{label=--}
% \setlist[itemize,2]{label=•}
% \setlist[itemize,3]{label=→}


\begin{document}

% Header
\begin{center}
    {\LARGE \textbf{Dongkwan Kim}} \\[2pt]
    Cybersecurity Engineer · AI Security \& Red Teaming · Vulnerability Research \\[4pt]
    \href{mailto:0xdkay@gmail.com}{\faEnvelope\ 0xdkay@gmail.com} \quad
    \href{https://0xdkay.me}{\faHome\ Homepage} \quad
    \href{https://scholar.google.com/citations?hl=ko&user=p16UJy8AAAAJ&view_op=list_works&sortby=pubdate}{\faGraduationCap\ Scholar} \quad
    \href{https://www.linkedin.com/in/0xdkay/}{\faLinkedin\ LinkedIn} \quad
    \href{https://github.com/0xdkay}{\faGithub\ GitHub}
    % \href{https://www.facebook.com/0xdkay}{\faFacebook\ Facebook}
\end{center}

% \begin{itemize}[label={}]
% \item \textbf{Cybersecurity Engineer}  with 10+ years of experience in vulnerability discovery and threat modeling.
% \end{itemize}
\begin{center}
\textit{Driving full-chain AI security, with a mission to build the next generation of Red Teams.}
\end{center}


% Professional Experience
\section{Professional Experience}
\begin{itemize}
\item \jobtitle{Postdoctoral Fellow}, \location{Georgia Tech | Atlanta, GA} \hfill \daterange{Feb 2025 -- Present}
    \begin{itemize}[] %label={}]
    \item DARPA AIxCC Finalist: Designed and implemented LLM-based autonomous fuzzing and exploit agents.
    % \item Contributing to 20\% of codebase (1500+ commits) in Team Atlanta
    \item Currently evaluating AI's offensive potential in real-world cybersecurity scenarios.
    \end{itemize}

\item \jobtitle{Senior Engineer}, \location{Samsung Security Center, Samsung SDS | Seoul, South Korea} \hfill \daterange{Aug 2022 -- Dec 2024}
    \begin{itemize}[] %label={}]
    \item Drove Red Team operations across AI systems, IoT devices, Android apps, and kernel-level mitigations.
        \begin{itemize}[] %label={}]
        \item Secured 30+ consumer and enterprise products, protecting 1B+ users.
        \item Delivered executive-level reports and gave organization-wide presentations to 500+ security engineers.
        \end{itemize}
    \item Shared insights on AI system security at 6 industry and academic venues.
        \begin{itemize}[]
        \item Securing prompt injection chains against remote code execution, impersonation, and sensitive data leak.
        \end{itemize}
    \end{itemize}

\item \jobtitle{Graduate \& Postdoctoral Researcher}, \location{KAIST | Daejeon, South Korea} \hfill \daterange{Mar 2014 -- Jul 2022}
    \begin{itemize}[] %label={}]
    \item Led 8-member research subgroup and conducted security research on emerging systems:
        \begin{itemize}[]
        \item Smartphones \& Android: Baseband auth bypass, AOSP privilege escalation, VoLTE exploitation.
        \item IoT \& Embedded Devices: Variant analysis on 1,100+ firmware, finding 20+ 0-days.
        \item Cellular Networks: LTE protocol attacks, policy bypass, free data tunneling.
        \item Drones \& Wearables: Acoustic/EMI attacks, sensor spoofing, wireless analysis.
        \end{itemize}
    \item Delivered 27 publications (9 top-tier venues, 1,100+ citations), 7 patents, and 17 funded projects.
    \item Discovered 100+ bugs in commercial systems, including Android and smartphone baseband 0-days.
    \end{itemize}

\item \jobtitle{Research Intern}, \location{Pinion Industries | Seoul, South Korea} \hfill \daterange{Dec 2013 -- Feb 2014}
    \begin{itemize}[] %label={}]
    \item Analyzed automotive CAN messages and exploited in-vehicle components, achieving RCE and wiretapping.
    \end{itemize}

\item \jobtitle{Student Senior}, \location{CERT, KAIST | Daejeon, South Korea} \hfill \daterange{Sep 2010 -- Aug 2012}
    \begin{itemize}[] %label={}]
    \item Led student team in campus-wide security audit, including probing a critical email attack leading to arrest.
    \end{itemize}
\end{itemize}

% Education
\section{Education}
\begin{itemize}[]
\item \jobtitle{Ph.D., School of Electrical Engineering}, \location{KAIST | Daejeon, South Korea} \hfill \daterange{Mar 2016 -- Feb 2022}
    \begin{itemize}[] %label={}]
    \item Advisor: Yongdae Kim
    \end{itemize}
\item \jobtitle{M.S., School of Electrical Engineering}, \location{KAIST | Daejeon, South Korea} \hfill \daterange{Mar 2014 -- Feb 2016}
    \begin{itemize}[] %label={}]
    \item Advisor: Yongdae Kim
    \end{itemize}
\item \jobtitle{B.S., Computer Science}, \location{KAIST | Daejeon, South Korea} \hfill \daterange{Mar 2010 -- Feb 2014}
\end{itemize}

% Technical Skills & Domains
\section{Additional Qualifications}
\begin{itemize}[itemsep=3pt]

\item \textbf{CTF Player:}
    5× DEF CON finalist, led 20-person team, organized Samsung CTF, \$115K+ total winnings.
\item \textbf{Community Contributor:}
    Delivered 20+ invited talks across academia and industry on emerging threats.
% \item Offensive Security: Red Team operations, penetration testing, threat modeling, vulnerability research
% \item Leadership: Cross-functional teams, executive reporting, multi-year roadmaps, CTF organization
% \item \textbf{AI Frameworks:} Exploit Agents - LangGraph, LangChain, LiteLLM, Phoenix ; Safety guardrail - PyRIT.
\item \textbf{AI Frameworks:} LangGraph, LangChain, LiteLLM, Phoenix (exploit agents); PyRIT (safety guardrails).
\item \textbf{Programming Languages:} Python, C/C++, Java, JavaScript.
\end{itemize}

\end{document}
